### 2021-06-15 paper/appendix_data.tex
Change K's comment color. Put rapid test params section in separate tex file and add text with URLs.

@@

Figure~\ref{fig:rapid_test_demand}\comment[id=J]{Talk about the interpretation of each line.}

In our model, there are five reasons why rapid tests are done:
\begin{enumerate}
    \item someone plans to have work contacts
    \item someone is an employees of an educational facility or school pupil
    \item someone lives in a household where someone has tested positive or developed
          symptoms
    \item someone has developed symptoms but has not received a PCR test
    \item someone plans to participate in a weekly non-work meeting
\end{enumerate}

% work rapid tests

For work contacts, we know from the COSMO study (\cite{Betsch2021}, 20th/21st of April)
that 60\% of workers who receive a test offer by their employer regularly use it. We
assume this share to be time constant.

In addition, there are some surveys that allow us to trace the expansion of employers who
offer tests to their employees. Mid march, 20\% of employers offered tests to their
employees \citep{DIHK2021}. In the second half of March, 23\% of employees reported being
offered weekly rapid tests by their employer \citep{Ahlers2021}. This share increased to
60\% until the first days of April \cite{ZDF2021}. Until mid April 70\% of workers were
expected to receive a weekly test offer \citep{AerzteZeitung2021}. However, according to
surveys conducted in mid April \citep{Betsch2021}, less than two thirds of individuals
with work contacts receive a test offer. Starting on April 19th employers were required
by law to provide two weekly tests to their employees \citep{Bundesanzeiger2021}. We
assume that compliance is incomplete and only 80\% of employers actually offer
tests.\comment[id=HM]{Can we use the IZA/BMAS survey? Not sur about citing evening news
in scientific papers.}\comment[id=K]{I am not aware of any survey looking at compliance.
If you know of some, that would be great. Updating this might change our results but it
would definitely be an improvement!}

% educ rapid tests

We assume that employees in educational facilities start getting tested in 2021 and that
by March 1st 30\% of them are tested weekly.

The share increases to 90\% for the week before Easter. At that time both Bavaria
\citep{BayrischerRundfunk2021} and Baden-Württemberg \citep{MinisteriumKultus2021} were
offering tests to teachers and North-Rhine Westphalia \cite{DPA2021} and Lower Saxony
\citep{SueddeutscheZeitung2021} were already testing students and tests for students and
teachers were already mandatory in Saxony \citep{SueddeutscheZeitung2021a}. After Easter
we assume that 95\% of teachers get tested twice per week.\comment[id=K]{Mostly newspaper
articles and one KuMi press communication. I have more sources for the smaller federal
states but they are extremely time consuming to enter into the references.}

% --------------------------------------------------------------------------------------
%
%def _add_educ_rapid_test_fade_in_params(params):
%    """Add the shares how many people with educ contacts get a rapid test.
%
%    Sources:
%        - 17-24 of March 2021 (Mon, 2021-03-22):
%            - NRW had 80% tests for students before Easter (https://bit.ly/3u7z8Rx)
%            - BY: test offers to educ_workers (https://bit.ly/3tbVX5u)
%            - BW: only tests for educ workers (https://bit.ly/2S7251M)
%
%            - federal level:
%                "In Kitas und Schulen sollen die Testmöglichkeiten "mit der
%                steigenden Verfügbarkeit von Schnell- und Selbsttests"
%                ausgebaut werden" (https://bit.ly/3nuCSKi)
%            - Some KiTa workers are being tested (https://bit.ly/3nyGyus)
%            - Self tests for students in Berlin (https://bit.ly/2ScGu8m)
%            - Schleswig-Holstein: test offer (https://bit.ly/3eVfkuv)
%            - mandatory tests in Saxony (https://bit.ly/3eEQGhn)
%            - no tests yet for students in Hessia, but already ordered
%              (https://bit.ly/3gMGJB4)
%            - Niedersachsen had one test week before Easter (https://bit.ly/3gOOC96)
%
%            => assume 90% of teachers and 40% of students do rapid tests
%
%        - After Easter (2021-04-07):
%            - NRW: tests are mandatory for all
%            - Bavaria: tests are mandatory for all (https://bit.ly/3nz5fXS,
%              https://bit.ly/2QHilX3)
%            - BW: voluntary tests for students (https://bit.ly/3vuetaD)
%            - Brandenburg starts with tests (https://bit.ly/3xAihZB)
%            - Schleswig-Holstein: mandatory tests (https://bit.ly/3eVfkuv)
%
%            => assume 95% of teachers and 75% of students get tested
%
%        - BW: tests mandatory starting 2021-04-19 (https://bit.ly/3vuetaD)
%
%            => assume 95% of teachers and 95% of students get tested
%
%    """
%    params = params.copy(deep=True)
%
%    loc = ("rapid_test_demand", "educ_worker_shares")
%    params.loc[(*loc, "2020-01-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-01-01"), "value"] = 0.0
%    # this is arbitrary to have a more convex shape
%    params.loc[(*loc, "2021-03-01"), "value"] = 0.3
%    params.loc[(*loc, "2021-03-22"), "value"] = 0.9
%    params.loc[(*loc, "2021-04-07"), "value"] = 0.95
%    params.loc[(*loc, "2021-04-19"), "value"] = 0.95
%    params.loc[(*loc, "2021-06-01"), "value"] = 0.95
%    params.loc[(*loc, "2025-12-31"), "value"] = 0.95
%
%    loc = ("rapid_test_demand", "student_shares")
%    params.loc[(*loc, "2020-01-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-02-01"), "value"] = 0.0
%    params.loc[(*loc, "2021-03-01"), "value"] = 0.1
%    params.loc[(*loc, "2021-03-22"), "value"] = 0.4
%    params.loc[(*loc, "2021-04-07"), "value"] = 0.75
%    params.loc[(*loc, "2021-04-19"), "value"] = 0.95
%    params.loc[(*loc, "2021-06-01"), "value"] = 1.0
%    params.loc[(*loc, "2025-12-31"), "value"] = 1.0
%
%    # Assume weekly tests before Easter and twice weekly tests after Easter
%    # We should get a fade-in through different ends of Easter vaccation
%    params.loc[("rapid_test_demand", "educ_frequency", "before_easter"), "value"] = 7
%    params.loc[("rapid_test_demand", "educ_frequency", "after_easter"), "value"] = 3
%
%    return params
%
% --------------------------------------------------------------------------------------

\comment[id=J]{Sources still missing below this}

Tests for students started later so we assume that they only start in February and only
10\% of students get tested by March 1st. Relying on the same sources as above we
approximate that by the week before Easter this share had increased to 40\%.

After Easter we assume the share of students receiving twice weekly tests to based on
tests already being mandatory in North-Rhine Westphalia and Bavaria while still being
voluntary in Baden-Württemberg. There tests become mandatory on April 19th.

% household member rapid tests

% own symptom rapid test demand

% private meeting test demand

\comment[id=J]{Add a section on how we calibrate rapid test demand; Mainly describe the
datapoints we have and say that we usually interpolate linearly in between data points.
(Only exception to that is private rapid test demand, which we fit to data)}

>>>>

\input{rapid_test_params}

All shares of individuals that would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.\comment[id=J]{Talk about the interpretation
of each line.}

@@
